\chapter*{\MakeUppercase{Acknowledgments}}
% \addcontentsline{toc}{chapter}{{\bf \MakeUppercase{Acknowledgments}}}


% Write your acknowledgments here.
% Expressing gratitude to contributors
The completion of this book, \emph{A Comprehensive Study of Machine Learning for Combinatorial Optimization}, would not have been possible without the support, guidance, and contributions of numerous individuals and organizations. I am deeply grateful to all who have played a role in bringing this work to fruition.

% Acknowledging academic and professional collaborators
First and foremost, I extend my heartfelt thanks to my colleagues and collaborators in the fields of machine learning and combinatorial optimization. Their insightful discussions, critical feedback, and shared expertise have significantly shaped the content and direction of this book. In particular, I am indebted to Dr. Jane Smith and Professor John Doe for their mentorship and encouragement throughout the research process.

% Recognizing institutional support
I am grateful to the Department of Computer Science at University Name for providing a stimulating academic environment and access to invaluable resources. The funding provided by the National Science Foundation and the Optimization Research Consortium enabled the exploration of advanced topics covered in this book. Their support for interdisciplinary research has been instrumental in advancing the integration of machine learning with optimization.

% Thanking technical and editorial teams
Special thanks go to the editorial team at Publisher Name for their professionalism and dedication. Their meticulous attention to detail and constructive suggestions greatly improved the clarity and presentation of the manuscript. I also appreciate the technical staff who assisted with computational experiments, particularly in the development of code and simulations for the case studies.

% Acknowledging personal support
On a personal note, I am profoundly thankful to my family and friends for their unwavering support and patience throughout this journey. Their encouragement provided the motivation to persevere through the challenges of writing this book. I dedicate this work to my parents, whose belief in the value of knowledge inspired my academic pursuits.

% Closing statement
Finally, I express my gratitude to the broader research community, whose collective efforts continue to push the boundaries of machine learning and combinatorial optimization. This book is a testament to the collaborative spirit of this field, and I hope it contributes to its ongoing advancement.


\newpage